Carbonate chemistry at Ny-Ålesund

### 2021-11-26 awipev-CO2.Rmd
removed commented code

```{r seafet profiles, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
# range <- d_all %>%
#   dplyr::mutate(pH_range_more_6m = ifelse(depth > 6, pHint_tot_sf, NA)) %>%
#   group_by(montht) %>%
#   summarize(pH_range = max(pHint_tot_sf, na.rm = TRUE) - min(pHint_tot_sf, na.rm = TRUE),
#             pH_range_more_6m = max(pH_range_more_6m, na.rm = TRUE) - min(pH_range_more_6m, na.rm = TRUE),
#             pH_range_more_9m = max(pHint_tot_sf_9m, na.rm = TRUE) - min(pHint_tot_sf_9m, na.rm = TRUE)) %>%
#   ungroup()
# print(kable(range, digits = 2))

# # datetime when pH values are in but no pressure data. File sent to send to Philipp
# no_pressure <- d_all %>% 
#   dplyr::select(datetime, depth, pHint_tot_sf) %>% 
#   dplyr::filter(is.na(depth) & !is.na(pHint_tot_sf))
# readr::write_csv(x = no_pressure, path=paste0(path,"/fb_awipev-co2_server/ny-alesund/data//no_pressure.csv"))

# tmp <- d_all %>% 
#   dplyr::select(montht, pHint_tot_sf, depth, depth_discrete) %>%
#   dplyr::group_by(depth, montht)
# p <- tmp %>% 
#   ggplot(aes(x=as.factor(depth), y = pHint_tot_sf)) +
#   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
#   labs(title = "pHT", x = "Depth (m)", y= "pHT") +
#   facet_wrap(vars(montht), scale = "free_y")
# print(p)
# 
# 
# p <- tmp %>% 
#   ggplot(aes(x=depth_discrete, y = pHint_tot_sf)) +
#   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
#   labs(title = "pHT", x = "Depth (m)", y= "pHT") +
#   facet_wrap(vars(montht), scale = "free_y")
# print(p)

# we look at all depths
tmp <- d_all %>% 
  dplyr::select(year, montht, pHint_tot_sf, depth_discrete) %>%
  tidyr::drop_na(pHint_tot_sf, depth_discrete) %>%
  dplyr::group_by(depth_discrete, year, montht)
summary(aov(tmp$pHint_tot_sf ~ tmp$depth_discrete * tmp$montht))

# remove outliers
quantile(tmp$pHint_tot_sf, na.rm =TRUE, probs = c(0.01, 0.99))

@@

pH is measured continuously by an autonomous durafet pH sensor. Final calibrated durafet pHT data (green doibb) are shown here after calibration with spectro measurements (red dots) according to each period of deployement, defined between 2 spectro measurements (shading grey). Calibration was done appliying an offset of pH between measured and spectro data per periods.

>>>>

```{r seafet profiles, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}

# we look at all depths
tmp <- d_all %>% 
  dplyr::select(year, montht, pHint_tot_sf, depth_discrete) %>%
  tidyr::drop_na(pHint_tot_sf, depth_discrete) %>%
  dplyr::group_by(depth_discrete, year, montht) %>% 
  dplyr::mutate(quant_01 = quantile(pHint_tot_sf, na.rm =TRUE, probs = c(0.05)),
                quant_99 = quantile(pHint_tot_sf, na.rm =TRUE, probs = c(0.95)),
                mean = mean(pHint_tot_sf, na.rm =TRUE),
                sd = sd(pHint_tot_sf, na.rm =TRUE)
                ) %>% 
  dplyr::filter(pHint_tot_sf < mean + sd, pHint_tot_sf > mean - sd) # remove outliers
#  dplyr::filter(pHint_tot_sf < quant_99, pHint_tot_sf > quant_01) # remove outliers
summary(aov(tmp$pHint_tot_sf ~ tmp$depth_discrete * tmp$montht))

@@

pH is measured continuously by an autonomous durafet pH sensor. Final calibrated durafet pHT data (green dots) are shown here after calibration with spectro measurements (red dots) according to each period of deployement, defined between 2 spectro measurements (shading grey). Calibration was done appliying an offset of pH between measured and spectro data per periods.
